Algomusicology, ???, Profit

### 2016-04-02 paper.tex
Fill out the rest of the argument.

(defmacro description-length [expression]
  (-> expression print-str count))

(fact
  (result-length (repeat 65 \G)) => 131
  (description-length (repeat 65 \G)) => 13)
\end{verbatim}

The explanatory power of a description can be measured by comparing the length of the textual description and the length
of the resulting value. Explanatory power is the reciprocal of the compression ratio, where representing a value by an
expression is viewed as a compression strategy.

If there is no way to describe a value more concisely than the value itself, we say that it is random. In other words an
explanatory power of one or less is no explanation at all.

\begin{verbatim}
(defmacro explanatory-power [expression]
  `(/ (result-length ~expression)
      (description-length ~expression)))

(fact
  (explanatory-power (repeat 65 \G)) => 131/13)
\end{verbatim}

@@

Lexicon's are interesting from a Kolmogorov complexity perspective, because they can be described concisely yet contain
multitudes. Paradoxically, lexicons display the property that the whole is simpler than (almost all of) the parts. That is,
the Kolmogorov complexity of all strings in our Library of Babel beyond a certain size are more complicated to describe
than the Library as a whole.

Borges appreciated this paradox. His anonymous narrator reports that on "some shelf in some hexagon (men reasoned)
there must exist a book which is the formula and perfect compendium of all the rest"?????. Any of the many books that contain
our library-of-babel function match the narrator's description, though the books that also contain the rest of this paper
must surely provide more helpful context.

@@

(defn champernowne-word
  ([from]
   (->> (range)
        (map (partial + from))
        (mapcat decompose-into-digits)))
  ([]
   (champernowne-word 0)))

(fact
  (->> (champernowne-word) (take 16))
    => [0 1 2 3 4 5 6 7 8 9 1 0 1 1 1 2])
\end{verbatim}

@@

@@

'Blurred Lines' is a pop song that was written by Pharrell Williams and Robin Thicke. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'.
\begin{verbatim}
(defn copyright-infringement-song
  ([skip-to]
   (->>
     (champernowne-word skip-to)
     (coding/decode 3)
     (where :time (bpm 120))
     (where :duration (bpm 120))))
   ([] (copyright-infringement-song 0)))

(def blurred-lines 12450012001200311273127612731276127312761273127612731276127312761245001200121245001200120031127312761273127612731276127312761273127612731276124500120012124500120012003112731276127312761273127612731276127312761273127612450012001212450012001200311273127612731276127312761273127612731276127312761245001200121240001200120031126812711268127112681271126812711268127112681271124000120012124000120012003112681271126812711268127112681271126812711268127112400012001212400012001200311268127112681271126812711268127112681271126812711240001200121252004100411264125012621249126112471245)
\end{verbatim}

@@

>>>>

(defmacro description-length [expression]
  (-> expression print-str count))
\end{verbatim}

Here is an example of using these definitions to calculate the description and result length of a short sequence of Gs.

\begin{verbatim}
(fact
  (result-length (repeat 65 \G)) => 131
  (description-length (repeat 65 \G)) => 13)
\end{verbatim}

The explanatory power of a description can be measured by comparing the length of the textual description and the length
of the resulting value. Explanatory power is equivalent to the compression power, where representing a value by an
expression is viewed as a compression strategy.

If there is no way to describe a value more concisely than the value itself, we say that it is random. In other words an
explanatory power of one or less is no explanation at all. In compression terms, there is no possible space saving
to be gained by representing this value by an expression.

\begin{verbatim}
(defmacro explanatory-power [expression]
  `(/ (result-length ~expression)
      (description-length ~expression)))
\end{verbatim}

The explanatory power of our expression for producing 65 Gs is high. A repetitive string of identical characters is
highly redundant, highly compressible and hence able to be described concisely. The explanatory power of this way of
representing the string of Gs this way is over 10.

\begin{verbatim}
(fact
  (explanatory-power (repeat 65 \G)) => 131/13)
\end{verbatim}

There are many expressions that evaluate to the same value, so there are likely to be different expressions of varying
explanatory power. The Kolmogorov complexity is defined as the length of the briefest possible description. This is not,
in general, computable, so it's not possible to determine whether we have obtained the best possible explanation for a
piece of data.

@@

Lexicons are interesting from a Kolmogorov complexity perspective, because they can be described concisely yet contain
multitudes. Paradoxically, lexicons display the property that the whole is simpler than (almost all of) the parts. That is,
the Kolmogorov complexity of all strings in our Library of Babel beyond a certain size are more complicated to describe
than the Library taken as a whole.

Borges appreciated this paradox. His anonymous narrator reports that on "some shelf in some hexagon (men reasoned)
there must exist a book which is the formula and perfect compendium of all the rest"?????. Any of the many books that contain
our \verb|library-of-babel| function match the narrator's description, though the books that also contain the rest of this paper
must surely provide more helpful context.

@@

(defn champernowne-word
  [skip-to]
  (->> (range)
       (map (partial + skip-to))
       (mapcat decompose-into-digits)))

(fact
  (->> (champernowne-word 0) (take 16))
    => [0 1 2 3 4 5 6 7 8 9 1 0 1 1 1 2])
\end{verbatim}

Here we generate the Champernowne word in the way that it is normally done. We start at zero, and decompose the digits of
every subsequent natural number. However, we could just as easily start at any other natural number, which is demonstrated
by the \verb|skip-to| argument. This is a useful property, because it lets us jump straight to any part of the constant
without having to generate all the previous digits.

@@

A notorious example. The British government of the time wished to discourage rave culture, so it passed legislation that banned
music with "repetitive beats"?????. Autechre responded with a track in which every bar features a unique beat?????.

@@

'Blurred Lines' is a pop song that was written by Pharrell Williams and Robin Thicke. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'.

As a response to this situation, I decided to compose a track that would infringe on the copyright of both songs. The following
piece decodes the Champernowne word into music.

\begin{verbatim}
(defn copyright-infringement-song
  [skip-to]
  (->>
    (champernowne-word skip-to)
    (coding/decode 3)
    (tempo (bpm 120))))
\end{verbatim}

As the Champernowne word's digits are predictable, I am able to skip ahead to any part of the song I choose. Here
is the value of \verb|skip-to| that results in a passable version of 'Blurred Lines'.\footnote{The encoding scheme is chosen
to be reversible, which allowed me to determine where in the Champernowne word 'Blurred Lines' would occur. Full details are in the accompanying code.}

\begin{verbatim}
(def gaye-williams-thicke-constant
  12450012001200311273127612731276127312761273127612731...
  27612731276124500120012124500120012003112731276127312...
  76127312761273127612731276127312761245001200121245001...
  20012003112731276127312761273127612731276127312761273...
  12761245001200121245001200120031127312761273127612731...
  27612731276127312761273127612450012001212400012001200...
  31126812711268127112681271126812711268127112681271124...
  00012001212400012001200311268127112681271126812711268...
  12711268127112681271124000120012124000120012003112681...
  27112681271126812711268127112681271126812711240001200...
  121252004100411264125012621249126112471245)
\end{verbatim}

There is nothing in the description of the \verb|copyright-infringement-song| that is in any way related to 'Blurred Lines'.
It is simply a straightforward musical rendering of a well-known mathematical constant derived from the decimal counting
system.

What's more, every other song is also somewhere in there.

Here we finally come to the profit generation strategy - copyright litigation. As the \verb|copyright-infringement-song| is
a universal piece of music, any work published subsequent to it infringes on its copyright.\footnote{I am not a lawyer. Do not rely on my legal advice.}

@@

\begin{enumerate}
    \item Algomusicology
    \item Copyright litigation
    \item Profit!
\end{enumerate}
